\documentclass[10pt,a4paper]{article}
\usepackage{minimalresume}
\usepackage{lmodern}

\begin{document}

\ResumeName{Sangwoo Kim}
\ContactInfo{+82 10 9772 7213}{sangwoo.kim.1003@gmail.com}


\ResumeSection{Education}
\ResumeEntry{Seoul National University}{Seoul, Korea}{
    \EducationEntry{B.S. in Computer Science and Engineering}{Dec 2023 -- Present}{}
}

\ResumeSection{Experience}
\ResumeEntry{Saccade Capital}{Seoul, Korea}{%
    \RoleEntry{Quantitative Analyst}{Dec 2023 -- Present}{%
        \item Develop and manage daily market-neutral long–short statistical arbitrage strategies in U.S. and Japan markets.
    }
}

\ResumeEntry{Schperics}{Seoul, Korea}{%
    \RoleEntry{Quantitative Researcher}{Oct 2021 -- Nov 2023}{%
        \item Developed a high-performance strategy simulator using Rust.
        \item Built research and trading infrastructure on AWS with Terraform.
        \item Designed a matrix-style data format that efficiently appends daily data for live trading.
    }
}

\ResumeEntry{KIDB Money Brokerage Co.}{Seoul, Korea}{%
    \RoleEntry{Project Manager}{Oct 2020 -- Oct 2021}{%
        \item Led design and development of a bond trading platform, including application architecture and business logic.
        \item Built AWS infrastructure using ECS, Lambda, and S3 with Terraform, ensuring financial regulatory compliance.
        \item Developed bond database management API in Python and front-end interfaces with Next.js and React.
        \item Filed three patents related to platform architecture and advanced order functionalities.
    }
}

\ResumeEntry{WorldQuant}{Seoul, Korea}{%
    \RoleEntry{Vice President, Research}{Jul 2020 -- Aug 2020}{%
        \item Led development of an in-house U.S. fundamental dataset that directly parses SEC filings, improving accuracy and retrieval speed.
        \item Standardized financial statement items across companies for consistent cross-firm analysis.
    }
    \RoleEntry{Senior Quantitative Researcher}{Jan 2018 -- Jul 2020}{%
        \item Worked closely with senior portfolio managers on a high-capacity, low-impact strategy, delivering alphas adopted for live trading.
        \item Developed and optimized a mean-variance based portfolio optimization algorithm in collaboration with a portfolio manager, published to the firm’s internal strategy marketplace.
        \item Advised global researchers on signal compositions and meta-strategy construction.
    }
    \RoleEntry{Quantitative Researcher}{Oct 2016 -- Jan 2018}{%
        \item Developed statistical arbitrage strategies across global markets, generating diversified alphas from a wide range of datasets, including fundamentals, analyst estimates, news, and social media.
        \item Designed filtering algorithms to select high-quality company alphas and combined them into meta-strategies.
    }
    \RoleEntry{Quantitative Developer}{Dec 2015 -- Oct 2016}{%
        \item Improved storage efficiency of in-house fundamental datasets by introducing intermediate data compression.
        \item Implemented monitoring system for daily data generation, identifying and resolving a critical data processing bug that caused missing values.
    }
}

\ResumeEntry{R.O.K. Cyber Command}{Seoul, Korea}{%
    \RoleEntry{Software Engineer}{Mar 2014 -- Dec 2015}{%
        \item Developed a real-time inter-unit chat service using Vert.x, Java, Scala, and AngularJS.
    }
}

\ResumeSection{Awards \& Honors}
\AwardsEntry{42nd Place}{The 35th Annual ACM-ICPC World Finals}{May 2011}{}
\AwardsEntry{Gold Medal}{The 10th Korean Collegiate Programming Contest}{Oct 2010}{}

\end{document}
